### 2015-03-11 article/article.tex
presentation initial commit

\begin{tabulary}{\linewidth}{ LLLLLL }

@@

	CAST/EiJ  & Rora (RAR-related orphan receptor alpha) & protein coding gene & trigonelline relative abundance &  8.8 

@@

	NZB/BlNJ & Nr1i3 (nuclear receptor subfamily 1, group I, member 3) & protein coding gene & [ECG parameters]interval between peak of P-wave to R-wave (PR) &  4.6\\ 

>>>>

\begin{tabulary}{\linewidth}{ LLLLL }

@@

	CAST/EiJ  & Rora (RAR-related orphan receptor alpha) & protein coding gene & trigonelline relative abundance &  8.8 \\

@@

	NZB/BlNJ & Nr1i3 (nuclear receptor subfamily 1, group I, member 3) & protein coding gene & ECG parameters interval between peak of P-wave to R-wave (PR) &  4.6\\ 
